### 2015-04-16 docs/ms.Rmd
Corrected figure 1 axis to change angle and integration time numbers. Minor changes throughout to correct spelling and remove & to keep consistent

Given that methodological variation may shape results in significant and unpredictable ways (Tables 1 & 2, and references therein), the comprehensive reporting of methods is a simple and crucial step in ensuring research is reproducible. Accordingly, we developed a list of information about the capture (Table 1) and analysis (Table 2) of colour data that should ideally be reported. With regards to the measurement of colour, we focus on the two most frequently used methods; photography and spectrometry. Analytical techniques are diverse, mathematically complex, and are being developed rapidly [@thery_insect_2010; @kelber_spectral_2010]. Such progress means that the need for a deep understanding of common methods can quickly outstrip the working knowledge of the average researcher. As a consequence, the subtle complexity of many analytical techniques can be overlooked by empiricists, leading to critical methodological information not being reported. Our guidelines for reporting the details of colour analyses (Table 2) thus cover two broad, common methods: colourimetric (or 'spectral') analyses, and visual modelling.

While we wish to emphasize that these details are essential to ensuring full reproducibility of data capture and analysis, we recognize that space restrictions in the main text of manuscripts may preclude the incorporation of all these details. In such cases, we suggest that details be included in meta-data or in a supplementary file so that the necessary information is available to researchers. It is also the case that there is variability in the degree to which each parameter may affect results, and so we have aimed to provide a brief, qualitative outline of the potential effects that variation in each parameter may have on the data (Table 1 & 2). These tables are not intended as a guide to the selection of methods, however, for which we refer readers to excellent recent reviews as well as the original publications [@stevens_using_2007; @kelber_animal_2003; @montgomerie_analyzing_2006; @kemp_integrative_2015, and references in Tables 1 & 2].

@@

Our literature survey suggests there is surprising inconsistency and incompleteness in commonly reported methodological details (Fig. 1). Most studies (`r specs+both`) used a spectrometer to measure colour, yet integration times (`r round(propSpec_fin["prop_int_time"], digits = 0)`% reported), and probe-sample geometry (`r round(propSpec_fin["prop_spec_angle"], digits = 1)`%) and distance (`r round(propSpec_fin["prop_spec_dist"], digits = 0)`%) were often not reported. Among studies that used photography (`r cam+both`), `r round(propCam_fin["prop_specpix_avg"], digits = 0)`% detailed the number of pixels averaged, though camera models were more frequently reported (`r round(camModel, digits = 0)`%). Light sources were detailed in `r round(propSpec_fin["prop_light_source"], digits = 0)`% and `r round(propCam_fin["prop_light_source"], digits = 0)`% of spectrometer- and camera-based studies, respectively. With regard to data analysis, of the `r analysisType[1]` studies that calculated colourimeteric variables, `r round(col_def, digits = 0)`% specifically defined their measure of brightness, hue and/or chroma. The receptor-noise limited model (Vorobyev et al. 1998) was commonly used among studies with visual modelling (`r vismod_type[3]` of `r sum(vismod_type)`), though there was considerable variation in the detailing of the type of receptor noise used (`r round(propSpec_fin["prop_vis_mod_noise_type"], digits = 0)`% reported), the type of quantum catch used (`r round(propSpec_fin["prop_vis_mod_qcatch"], digits = 0)`%), or whether photoreceptor adaptation (`r round(propSpec_fin["prop_vis_mod_adapt"], digits = 0)`%) was modelled. In contrast, details of the species’ visual system being modelled (`r round(propSpec_fin["prop_vis_mod_sp"], digits = 0)`%), the background used (`r round(propSpec_fin["prop_vis_mod_bkg"], digits = 0)`%), and the modelled illuminant (`r round(propSpec_fin["prop_irrad_type"], digits = 0)`%) were more commonly reported.

@@

Our review of the recent literature highlights some impediments to reproducibility in the study of biological colourationcoloration. The simplest step towards reproducible research is through the comprehensive reporting of methods, yet key information is often unreported (Fig. 1). Here we provide a list of methodological information that we suggest be specified in studies that focus on the spectrometric- or camera-based analysis of colour (Tables 1 & 2). In addition to the suggested information, we also recommend that raw spectra be presented where possible, as these figures allow for the rapid assessment of the nature and quality of the data independent of downstream processing. We also emphasise the importance of explicitly outlining the biological justification underlying all choices for data capture and analysis [@kemp_integrative_2015]. Finally, the public storage of data along with detailed meta-data plays a pivotal role in reproducibility, yet public data storage in studies of colour traits is not yet the norm. We therefore encourage researchers to consider the substantial benefits of publicly archiving their data [@whitlock_data_2011; @piwowar_sharing_2007]. Overall, we hope that our guidelines will encourage researchers to think about the reproducibility of their work and the advantages of increased transparency, which will continue the advance of an exciting era in colour research.

>>>>

Given that methodological variation may shape results in significant and unpredictable ways (Tables 1 and 2, and references therein), the comprehensive reporting of methods is a simple and crucial step in ensuring research is reproducible. Accordingly, we developed a list of information about the capture (Table 1) and analysis (Table 2) of colour data that should ideally be reported. With regards to the measurement of colour, we focus on the two most frequently used methods; photography and spectrometry. Analytical techniques are diverse, mathematically complex, and are being developed rapidly [@thery_insect_2010; @kelber_spectral_2010]. Such progress means that the need for a deep understanding of common methods can quickly outstrip the working knowledge of the average researcher. As a consequence, the subtle complexity of many analytical techniques can be overlooked by empiricists, leading to critical methodological information not being reported. Our guidelines for reporting the details of colour analyses (Table 2) thus cover two broad, common methods: colourimetric (or 'spectral') analyses, and visual modelling.

While we wish to emphasize that these details are essential to ensuring full reproducibility of data capture and analysis, we recognize that space restrictions in the main text of manuscripts may preclude the incorporation of all these details. In such cases, we suggest that details be included in meta-data or in a supplementary file so that the necessary information is available to researchers. It is also the case that there is variability in the degree to which each parameter may affect results, and so we have aimed to provide a brief, qualitative outline of the potential effects that variation in each parameter may have on the data (Table 1 and 2). These tables are not intended as a guide to the selection of methods, however, for which we refer readers to excellent recent reviews as well as the original publications [@stevens_using_2007; @kelber_animal_2003; @montgomerie_analyzing_2006; @kemp_integrative_2015, and references in Tables 1 and 2].

@@

Our literature survey suggests there is surprising inconsistency and incompleteness in commonly reported methodological details (Fig. 1). Most studies (n = `r specs+both`) used a spectrometer to measure colour, yet integration times (`r round(propSpec_fin["prop_int_time"], digits = 0)`%), and probe-sample geometry (`r round(propSpec_fin["prop_spec_angle"], digits = 0)`%) and distance (`r round(propSpec_fin["prop_spec_dist"], digits = 0)`%) were often not reported. Among studies that used photography (n = `r cam+both`), `r round(propCam_fin["prop_specpix_avg"], digits = 0)`% detailed the number of pixels averaged, though camera models were more frequently reported (`r round(camModel, digits = 0)`%). Light sources were detailed in `r round(propSpec_fin["prop_light_source"], digits = 0)`% and `r round(propCam_fin["prop_light_source"], digits = 0)`% of spectrometer- and camera-based studies, respectively. With regard to data analysis, of the `r analysisType[1]` studies that calculated colourimeteric variables, `r round(col_def, digits = 0)`% specifically defined their measure of brightness, hue and/or chroma. The receptor-noise limited model (Vorobyev et al. 1998) was commonly used among studies with visual modelling (`r vismod_type[3]` of `r sum(vismod_type)`), though there was considerable variation in the detailing of the type of receptor noise used (`r round(propSpec_fin["prop_vis_mod_noise_type"], digits = 0)`% reported), the type of quantum catch used (`r round(propSpec_fin["prop_vis_mod_qcatch"], digits = 0)`%), or whether photoreceptor adaptation (`r round(propSpec_fin["prop_vis_mod_adapt"], digits = 0)`%) was modelled. In contrast, details of the species’ visual system being modelled (`r round(propSpec_fin["prop_vis_mod_sp"], digits = 0)`%), the background used (`r round(propSpec_fin["prop_vis_mod_bkg"], digits = 0)`%), and the modelled illuminant (`r round(propSpec_fin["prop_irrad_type"], digits = 0)`%) were more commonly reported.

@@

Our review of the recent literature highlights some impediments to reproducibility in the study of biological coloration. The simplest step towards reproducible research is through the comprehensive reporting of methods, yet key information is often unreported (Fig. 1). Here we provide a list of methodological information that we suggest be specified in studies that focus on the spectrometric- or camera-based analysis of colour (Tables 1 and 2). In addition to the suggested information, we also recommend that raw spectra be presented where possible, as these figures allow for the rapid assessment of the nature and quality of the data independent of downstream processing. We also emphasise the importance of explicitly outlining the biological justification underlying all choices for data capture and analysis [@kemp_integrative_2015]. Finally, the public storage of data along with detailed meta-data plays a pivotal role in reproducibility, yet public data storage in studies of colour traits is not yet the norm. We therefore encourage researchers to consider the substantial benefits of publicly archiving their data [@whitlock_data_2011; @piwowar_sharing_2007]. Overall, we hope that our guidelines will encourage researchers to think about the reproducibility of their work and the advantages of increased transparency, which will continue the advance of an exciting era in colour research.
